TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-11-28 paper/draft.tex
move caption details to text

\thecannon\ model can in principle be trained on any physical or empirical labels available, giving a wide range of flexibility to the model. However choosing a training sample with high quality labels is critical to the performance of \thecannon.
Limitations of \thecannon\ include that test (output) labels are only accurate if the training labels are accurate, and only precise if the training labels are measured consistently across the training sample.
Also, it is critical to have a training sample with the dynamic range to span the entire parameter space of interest, as \thecannon\ does not extrapolate well outside the parameter space of the training sample.
Finally, \thecannon\ deeply assumes that the dependence of spectrum on labels is continuous and smooth---and in this implementation, well approximated by quadratic functions---if that isn't true, there will be features that \thecannon\ cannot reproduce.

@@

@@

%---------------------------
\begin{figure}[ht]
\plotone{figures/aspcap_cannon_validation.png}
\caption{\cannon\ (right column) and \aspcap\ (left column) temperatures as compared to temperatures estimated from visible and infrared color-temperature relations from three different literature sources for a subsample of 6,257 sources. Shown are \cannon\ and \aspcap\ temperatures (x-axis) compared to temperatures estimated from the \citealt{Mann:2015} $V-J$ and [Fe/H] dependent relation (top), \citealt{Casagrande:2008} $V-K$ relation (middle), and the \citealt{Boyajian:2012} relation (bottom). We find \aspcap\ overestimates \teff\ on average by about 130K for the M15 and B13 relations about 220K for the C08. Additionally we see the scatter much higher for the \aspcap\ temperatures ($\sim220$K) compared to the scatter of \cannon\ temperatures ($\sim80-100$K), the scatter for both \aspcap\ and \cannon\ temperatures largely due to variation in metallicity.  \label{fig:teff_comparisons}}
\end{figure}

>>>>

\thecannon\ model can in principle be trained on any physical or empirical labels available, giving a wide range of flexibility to the model. However choosing a training sample with high quality labels is critical to the performance of \thecannon.
Limitations of \thecannon\ include that test (output) labels are only accurate if the training labels are accurate, and only precise if the training labels are measured consistently across the training sample.
Also, it is critical to have a training sample with the dynamic range to span the entire parameter space of interest, as \thecannon\ does not extrapolate well outside the parameter space of the training sample.
Finally, \thecannon\ assumes that the dependence of spectrum on labels is continuous and smooth---and in this implementation, well approximated by quadratic functions---if that isn't true, there will be features that \thecannon\ cannot reproduce.

@@

We find \aspcap\ overestimates \teff\ on average by $130-170$K, while \thecannon\ underestimates \teff\ by $\sim25$K . We also see the scatter is much higher for the \aspcap\ temperatures ($\sim230$K) compared to the scatter of \cannon\ temperatures ($\sim85$K).

@@

%---------------------------
\begin{figure}[ht]
\plotone{figures/aspcap_cannon_validation.png}
\caption{\cannon\ (right column) and \aspcap\ (left column) temperatures as compared to temperatures estimated color-temperature relations from three different literature sources for a subsample of 6,257 sources with $V,J,K$ colors. Shown are \cannon\ and \aspcap\ temperatures (x-axis) compared to temperatures estimated from the \citealt{Mann:2015} $V-J$ and [Fe/H] dependent relation (top), \citealt{Casagrande:2008} $V-K$ relation (middle), and the \citealt{Boyajian:2012} relation $V-K$ and [Fe/H] (bottom).  \label{fig:teff_comparisons}}
\end{figure}
